\chapter{Summary}
This project presents a novel proprietary 3D object detection model that demonstrates exceptional performance in terms of accuracy and efficiency. We introduce a cutting-edge model to address existing approaches' limitations and advance 3D object detection. Modern 3D detection models are based on advanced deep convolution neural networks. Our architecture is a hybrid approach using both analytical algorithms and neural networks.

Documentation begins with an overview of state-of-the-art solutions. It shows many different approaches to 3D object detection and emphasises the need for improved accuracy in detecting objects in three-dimensional space while ensuring real-time processing capabilities.

The proprietary model utilises innovative deep learning architectures and optimised algorithms. We describe the unique architectural design, which incorporates convolutional neural networks and analytical algorithms to get performance as good as possible regarding frame rate and accuracy. 

The \textit{Instance Segmentation} project was a valuable learning experience for the entire team. While working on it, we had to face different problems, both of technical and personal nature. We had to deal with problems concerning changes in the team members, both in the beginning and middle of the project and with the lab equipment not working properly.

Despite the project team's hardship during its development, we are satisfied with the results. Ultimately, we delivered a working program that fulfils all initial assumptions and leaves room for further development. While we are content, we realise some aspects of our program could be improved. We would be glad to work on these improvements in the future.
